TG2 Publications

### 2025-04-16 papers.qmd
Update papers.qmd with TG2 Content

<details>
  <summary>Click for Answer</summary>
Test Test
</details>

@@

[Link] (https://diagnprognres.biomedcentral.com/articles/10.1186/s41512-020-00074-3)

@@

[Link] (https://bmcmedresmethodol.biomedcentral.com/articles/10.1186/s12874-019-0666-3)

@@

[Link] (https://stratos-initiative.org/sites/default/files/STRATOS-TG2-BB-variable-selection.pdf)

@@

[Link] (https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0241427)

@@

* Lu Z, Lou W. Bayesian approaches to variable selection: a comparative study from practical perspectives. Int J Biostat 2021; [https://doi.org/10.1515/ijb-2020-0130] (https://doi.org/10.1515/ijb-2020-0130)

>>>>

@@

[Link](https://diagnprognres.biomedcentral.com/articles/10.1186/s41512-020-00074-3)

@@

[Link](https://bmcmedresmethodol.biomedcentral.com/articles/10.1186/s12874-019-0666-3)

@@

[Link](https://stratos-initiative.org/sites/default/files/STRATOS-TG2-BB-variable-selection.pdf)

@@

[Link](https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0241427)

@@

* Lu Z, Lou W. Bayesian approaches to variable selection: a comparative study from practical perspectives. Int J Biostat 2021; [https://doi.org/10.1515/ijb-2020-0130](https://doi.org/10.1515/ijb-2020-0130)
